---
title: "Analysis of *Nobel Prize laureates* dataset"
date: "January 2023"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r libraries, include=FALSE}
rm(list=ls())

library(dplyr)
library(ggplot2)
library(ggthemes)
library(ggpubr)

library(wordcloud)
library(RColorBrewer)
library(tm)

library(RWeka)
```

```{r ggplot_theme_setup, include=FALSE}
theme_set(
  theme_gdocs() + 
    theme(legend.position = "bottom", legend.direction="horizontal", legend.title = element_blank(), legend.text = element_text(size = 17),
          plot.title = element_text(hjust = 0.5, size = 20), plot.subtitle = element_text(hjust = 0.5, size = 16),
          axis.text=element_text(size=16),
          axis.title.x = element_text(size = 18),
          axis.title.y = element_text(size = 18, lineheight = 1),
          panel.grid.major = element_line(linetype = 3, colour = "grey62"),
          plot.background = element_rect(color = "white"))
)
```


# Dataset insight
Data used in this project comes from *public.opendatasoft.com* website and it includes Nobel Prizes from the very 1901 to last year - 2022.

At the beginning, let's take a look at the dataset by checking the column names.

```{r read_data, include=FALSE}
data <- read.csv(file = "C:/Users/Ola/Desktop/Nobel/nobel-prize-laureates_working.csv",
                 header = TRUE)
data <- data %>% mutate(Gender = ifelse(Gender == "org", "organization",Gender))
```

```{r column_names, echo=FALSE}
colnames(data)
```
There are plenty of columns with both - numerical and text - values. In this case study I focused mostly on succeeding variables:

* Category - category the Prize was awarded at,
* Gender - gender of the laureate,
* Born - year when the laureate was born,
* Year - year when Nobel Prize was awarded,
* Age - calculated as a difference between *Year* and *Born* values,
* Born.country - place of birth of the laureate,
* Organization - place of work of the laureate,
* Motivation - argumentation for awarding the laureate.

Below you can find data analysis and some visualizations grouped in five sections:

* [General statistics](#General-statistics),
* [Gender](#Gender),
* [Age](#Age),
* [Background](#Background),
* [Prize motivation](#Prize-motivation).

Please enjoy!

O.

\newpage
# General statistics {#General-statistics}

The Nobel Prize laureates have been selected since
```{r first_year, echo=FALSE}
data$Year[1]
```
and there are 6 categories:
```{r category_print, echo=FALSE}
sort(unique(data$Category))
```
In the table below years when the Prizes started to be awarded are presented:
```{r first_year_category, echo=FALSE}
data %>%
  group_by(Category) %>%
  summarize(`First Year to be awarded` = min(Year)) %>%
  knitr::kable() 
```
Not for all of the categories the Prizes were awarded from the very beginning. It started with 5 of current 6 categories. The youngest category - Economics - was added almost 70 years later.

Let's take a look at the categories the Nobel Prizes were presented at through the years:

```{r plot1_awarding_across_the_years, echo=FALSE, fig.width=12,fig.height=5}
data_plot_0 <- data %>% distinct(Year, Category, .keep_all = TRUE) %>% mutate(award = "awarded") 
ggplot(data = data_plot_0, aes(x = Year, y = award, color = "indianred3")) +
  geom_point(shape = 3, size = 3) +
  labs(x = "years", y = "prize awarded") +
  ggtitle("Nobel Prize awarding across the years")+
  facet_grid(rows = vars(Category)) +
  theme(axis.text.y=element_blank(),
        legend.position = "none",
        strip.text.y = element_text(angle = 0, size = 15))
```

There is a noticable break of **3** years in Prize awarding from 1940 to 1942. 

Since **1973** Prizes are always presented in all six categories.

\newpage
Years when Prizes were awarded in least number of categories: 
```{r years_with_least_awards, echo=FALSE, message=FALSE}
subset1 <- data %>%
  group_by(Year, Category) %>%
  summarize(n = n())

subset1 <- subset1 %>%
  group_by(Year) %>%
  summarize(`Number of categories` = n()) %>%
  arrange(`Number of categories`) %>%
  head(2)

Category <- c("Literature", "Chemistry, Physics")
subset1 %>% 
  mutate(Category = Category) %>%
  knitr::kable()
```

Moreover, number of laureates has been changing throughout the years as well:

```{r plot2_number_of_laureates_across_years, echo=FALSE, fig.width=12,fig.height=5}
for_number_of_laureates_across_years <- data %>% group_by(Year) %>% summarize(n = n())

number_mean  <- aggregate(for_number_of_laureates_across_years$n, 
                       by=list(cut(for_number_of_laureates_across_years$Year,seq(1901,2022,10))),
                       mean, na.rm = TRUE) 

number_mean <- number_mean %>% mutate(Year = as.numeric(sub("].*", "", sub(".*,", "", number_mean$Group.1))) - 10/2)

ggplot(data=for_number_of_laureates_across_years, aes(x=Year, y=n, group=1)) +
  geom_point(color="indianred2", size = 3) +
  labs(x = "year", y = "number of laureates") +
  ggtitle("Annual number of Nobel Prize laureates\nacross the years") +
  ylim(c(0,15)) +
  geom_point(data = number_mean, aes(x = Year, y = x), color = "black", size = 1) +
  geom_line(data = number_mean, aes(x = Year, y = x), color = "black", size = 0.8, linetype = "dashed") 

```

There is a observable increase of number of annually awarded laureates. 

Years with most laureates: **2001** (15), **2019** (14) and **2022** (14).

Years with least laureates: **1916** (1), **1918** (2), **1914** (3) and **1924** (3).

Now, let's take a closer look at yearly statistics of number of winners in each category:
```{r stats_of_number_of_laureates_category, echo=FALSE,message=FALSE}
for_avg_number_of_winners <- data %>%
  group_by(Year, Category) %>%
  summarise(n = n())
  
for_avg_number_of_winners %>% 
  group_by(Category) %>%
  summarize(`Average` = round(mean(n),1),
            `Median` = median(n),
            `Maximum` = max(n)) %>%
  knitr::kable() 
```

In each category total numbers of laureates are:

```{r total_number_of_laureates_category, echo=FALSE}
data %>% 
  group_by(Category) %>%
  summarize(`Total number of laureates` = n()) %>%
  arrange(`Total number of laureates`) %>%
  knitr::kable() 
```

\newpage
There are laureates who were awarded more than once:

```{r multiple_laureates, echo=FALSE, message=FALSE}
subset2 <- data %>%
  mutate(`Full Name` = paste(Firstname, Surname, sep = " "), .after = Surname) %>%
  group_by(`Full Name`) %>%
  summarize(`Nobel Prizes` = n(), `Prize year` = Year, `Category` = Category, `Age` = Age) %>%
  arrange(desc(`Nobel Prizes`)) %>%
  head(n = 15) 

subset2 %>%
  select(`Full Name`, `Prize year`, `Category`, `Age`) %>%
  knitr::kable()
```

Fun fact - most popular names among the Nobelists are:

```{r most_popular_names, echo=FALSE}
for_most_popular_name <- data %>%
  group_by(Firstname) %>%
  summarize(`Number of laureates` = n()) %>%
  arrange(desc(`Number of laureates`)) %>%
  head(n = 50) %>%
  distinct(Firstname, .keep_all = TRUE)

for_most_popular_name %>% 
  select(Firstname, `Number of laureates`) %>%
  head(5) %>%
  knitr::kable() 
```

However, there are not 12 but 11 different Johns, because John Bardeen is a double Nobel laureate. Considering the popularity of John name, let's view the countries all Johns were born in:

```{r John_born_country, echo=FALSE}
data %>%
  filter(Firstname == "John") %>%
  mutate(`Full Name` = paste(Firstname, Surname, sep = " "), .after = Surname) %>%
  select(`Full Name`, Born.country) %>%
  distinct(`Full Name`, .keep_all=TRUE) %>%
  knitr::kable()

```


\newpage
# Gender {#Gender}
At the beginning, let's look how many women and men there are among all laureates:

```{r genders_among_winners, echo=FALSE}
data %>%
  group_by(Gender) %>%
  summarize(`Number of winners` = n()) %>%
  knitr::kable()

```

Women Nobelists represent **6.4%** of all winners. And within all categories:

```{r plot3_gender_share, echo=FALSE, fig.width=12,fig.height=5, message=FALSE}
for_gndr_share_plot <- data %>%
  group_by(Category, Gender) %>%
  summarise(n = n())

for_gndr_share_plot <- for_gndr_share_plot %>%
  mutate(per =  100*n/sum(n))

for_gndr_share_plot$Gender <- factor(for_gndr_share_plot$Gender, levels = c("male", "female", "organization"))
ggplot(for_gndr_share_plot, aes(fill=Gender, y=per, x=Category)) + 
  geom_bar(position="stack", stat="identity", width = 0.55) + 
  ggtitle("Percentage share of genders among Nobel laureates") +
  scale_y_continuous(labels = function(x) paste0(x, "%")) +
  labs(x = NULL, y = NULL) +
  scale_fill_manual(values = c("#F6A682", "#D85C26", "#AE3F20")) +
  theme(panel.grid.major.x = element_blank())
```

First year when women were prized in all categories:

```{r first_year_to_prize_a_woman, echo=FALSE}
#data <- data %>% mutate(Surname = ifelse(Firstname=="Selma","Lagerlof",Surname))

data %>%
  filter(Gender == "female") %>%
  group_by(Category) %>%
  mutate(first_year = min(Year)) %>%
  select(Firstname, Surname, Year, Category) %>%
  filter(row_number()==1) %>% 
  arrange(Category) %>%
  knitr::kable()
```

Marie Curie is the youngest woman Nobelist in two categories and at all. 

In below table you can see years, when most women were awarded with comparison to all laureates:

```{r most_women_prized, echo=FALSE, message=FALSE}
#years_most_women <- c("2009","2011","2018","2020","2004")
# 
# data %>%
#   filter(years_most_women %in% Year) %>%
#   group_by(Year) %>%
#   summarize(n=n())
subset3 <- data %>% 
  filter(Gender == "female") %>%
  group_by(Year) %>%
  summarize(`Awarded women`=n()) %>%
  arrange(desc(`Awarded women`)) %>%
  head(5)

years_most_women <- c(2009,2011,2018,2020,2004)
all_winners_in_these_years <- c(13,13,13,12,12)
subset_df <- data.frame(cbind(Year=years_most_women, All=all_winners_in_these_years))

subset3 %>%
  left_join(subset_df) %>%
  arrange(desc(`Awarded women`), desc(`Year`)) %>%
  knitr::kable()
```

There are multiple years when women were not awarded at all. For **119** years of Nobel Prizes, 
at least one woman was awarded **42** times. It gives **77** times with only men being awarded (**65.7%**).

\newpage
# Age {#Age}

Now, let's see some statistics for the Nobelists' age.

Oldest laureates:
```{r eldest_laureates, echo=FALSE}
data %>% 
  select(Firstname, Surname, Year, Age, Category) %>%
  arrange(desc(Age))%>%
  head(7) %>%
  knitr::kable()
```

Youngest laureates:
```{r youngest_laureates, echo=FALSE}
youngest <- data %>% 
  select(Firstname, Surname, Year, Age, Category) %>%
  arrange(Age) %>%
  head(8)

youngest <- youngest[-c(1,8),]
rownames(youngest) <- NULL
youngest %>% 
  knitr::kable()
```

Below chart presents the comparison between youngest and oldest men and women Nobelists in all categories:

```{r plot4_oldest_youngest_laureates_by_gender_and_cat, echo=FALSE, fig.width=12,fig.height=6}
data_age <- data %>% filter(Gender != "organization")

oldest <- data_age %>% 
  group_by(Gender, Category) %>%
  filter(Age == max(Age, na.rm = TRUE)) %>%
  select(Gender, Category, Firstname, Surname, Age) %>%
  arrange(desc(Age), desc(Gender))

oldest$where <- rep("oldest", nrow(oldest))

youngest <- data_age %>% 
  group_by(Gender, Category) %>%
  filter(Age == min(Age, na.rm = TRUE)) %>%
  select(Gender, Category, Firstname, Surname, Age) %>%
  arrange(desc(Age), desc(Gender))

youngest$where <- rep("youngest", nrow(youngest))
youngest$Age <- youngest$Age*(-1)

the_data <- rbind(oldest,youngest)

gg_youngest <- ggplot(data = the_data, aes(x = Age, y = Category, fill = Gender)) + 
  geom_bar(data = subset(the_data, where == "youngest"), stat = "identity", position = "dodge", width = 0.7) +
  scale_fill_manual(values = c("#D85C26", "#F6A682")) + 
  scale_x_continuous(breaks = seq(-60,0,10), labels = abs(seq(-60,0,10)), limits = c(-60,0))  + 
  labs(x="age")+
  ggtitle("Youngest laureates") +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.margin=unit(c(0.1,0.2,0.1,-.1),"lines"),
        plot.background = element_rect(color = "white"))

gg_oldest <- ggplot(data = the_data, aes(x = Age, y = Category, fill = Gender)) + 
  geom_bar(data = subset(the_data, where == "oldest"), stat = "identity", position = "dodge", width = 0.7) +
  scale_fill_manual(values = c("#D85C26", "#F6A682")) + 
  scale_x_continuous(breaks = seq(0,100,10), labels = abs(seq(0,100,10)), limits = c(0,100))   + 
  labs(x="age")+
  ggtitle("Oldest laureates") +
  theme(axis.text.y = element_text(size=15,hjust=0.5), 
        axis.title.y = element_blank(), 
        plot.margin=unit(c(0.1,0,0.1,0.05),"lines"),
        panel.background = element_rect(color = "white"),
        panel.grid = element_blank(),
        plot.background = element_rect(color = "white")) 

ggarrange(gg_youngest, gg_oldest, 
          nrow = 1, ncol=2, 
          widths=c(0.4,0.6),
          common.legend = TRUE, legend = "bottom")
```

\newpage

In below table, you can see statistics for laureates' **age** in each category:

```{r stats_for_age_of_laureates, echo=FALSE}
data %>%
  group_by(Category) %>%
  summarize(`Mean` = round(mean(Age, na.rm = TRUE),1), 
            `Median` = median(Age, na.rm = TRUE),
            `Stand dev` = round(sd(Age, na.rm = TRUE),1)) %>%
  knitr::kable()
```

Average age of Nobel Prize winner is **56**.

Histogram of laureates' age:

```{r plot5_age_histogram, echo=FALSE, fig.width=12,fig.height=4, warning=FALSE, message = FALSE}
data_hist <- data %>% filter(Gender != "organization")
ggplot(data = data_hist, aes(x = Age)) +
  geom_histogram(binwidth  = 10, boundary = 0, fill = "#D85C26", color = "lightgrey") +
  ggtitle("Age of Nobel Prize laureates") +
  labs(x = "age", y = "counts") + 
  scale_x_continuous(breaks = seq(0,100,10), minor_breaks = seq(10,100,10), limits = c(0,100)) +
  ylim(c(0,300))
```

And after dividing into categories:

```{r plot6_age_histogram_by_cat, echo=FALSE, fig.width=12,fig.height=6, warning=FALSE}
ggplot(data = data_hist, aes(x = Age, fill = Category)) +
  geom_histogram(aes(y = ..density..), binwidth = 10, boundary = 0, color = "lightgrey") +
  facet_wrap(~Category, scales = "free") + 
  scale_x_continuous(breaks = seq(0,100,10), minor_breaks = seq(10,100,10), limits = c(0,100)) +
  scale_y_continuous(breaks = seq(0,0.05,0.01), minor_breaks = seq(0,0.05,0.01), limits = c(0,0.052)) +
  ggtitle("Age of Nobel Prize laureates", subtitle = "by category") +
  labs(x = "age", y = "density") +
  scale_fill_manual(values = c("coral", "coral1", "tomato","tomato2", "indianred2", "indianred3")) +
  theme(legend.position = "none",
        strip.text.x = element_text(hjust = 0.5, size = 17))
```

\newpage
We can also see how the age of laureates in each category has been changing through the years:

```{r plot7_age_across_years, echo=FALSE, fig.width=12,fig.height=7, warning=FALSE}
data_age_plot <- data %>% filter(Gender != "organization")

age_mean  <- aggregate(data_age_plot$Age, 
                       by=list(Category = data_age_plot$Category, cut(data_age_plot$Year,seq(1901,2022,10))), 
                       mean, na.rm = TRUE) 

age_mean <- age_mean %>% mutate(Year = as.numeric(sub("].*", "", sub(".*,", "", age_mean$Group.2))) - 10/2)

ggplot(data = data_age_plot, aes(x = Year, y = Age, color = Category)) +
  geom_point(alpha = 0.6, size = 2, shape = 19) + 
  scale_y_continuous(limits = c(0,100), breaks = seq(0,100,20)) +
  scale_x_continuous(limits = c(1900,2025), breaks = seq(1900,2025,25)) +
  facet_wrap(~Category, scales = "free") + 
  scale_color_manual(values = c("coral", "coral1", "tomato","tomato2", "indianred2", "indianred3")) +
  ggtitle(paste0("Age of Nobel Prize laureates","\n" ,"across the years"), subtitle = "by category") +
  labs(x = "year", y="age") +
  geom_point(data = age_mean, aes(x = Year, y = x), color = "black", size = 1.2) +
  geom_line(data = age_mean, aes(x = Year, y = x), color = "black", size = 0.8) +
  theme(legend.position = "none",
        strip.text.x = element_text(hjust = 0.5, size = 17))
```

There is a visible **increase** for **Chemistry**, **Physics** and **Medicine** and **decrease** for **Peace**.

\newpage
# Background {#Background}
The dataset gives an opportunity to see were the Nobelists come from, by country and by research unit.

Most laureates were born in:

(note: born does not equal nationality)

```{r most_popular_born.ctry, echo=FALSE}
data %>%
  group_by(Born.country) %>%
  summarize(`Number of laureates` = n()) %>%
  arrange(desc(`Number of laureates`)) %>%
  head(10) %>%
  knitr::kable()
```

People born in United States of America make up a significant percentage of all laureates. Let's take a look at years when most of them were prized:

```{r most_americans_awarded, echo=FALSE}
subset4 <- data %>%
  filter(Born.country == "USA") %>%
  group_by(Year) %>%
  summarize(`Number of USA-born laureates`=n()) %>%
  arrange(desc(`Number of USA-born laureates`)) %>%
  head() 

subset4$All <- c(11,11,15,8,11,12)
subset4 %>%
  knitr::kable()
```

Although, there is no year with only American laureates awarded.

We can also find out, what universities most laureates are connected with:

```{r most_awarded_organizations, echo=FALSE}
data %>%
  group_by(Organization.name) %>%
  summarize(`Scientific unit` = n()) %>%
  arrange(desc(`Scientific unit`)) %>%
  head() %>%
  knitr::kable()
```

\newpage
# Prize motivation {#Prize-motivation}

The last section in this report is the Prize motivation. For each category I carried out analysis of the motivation text by counting the frequency of appearance of words. The results are presented below in form of **word clouds**:

```{r wordclouds_code, include=FALSE, echo=FALSE}
text_peace <- data %>% filter(Category == "Peace") %>% select(Motivation)
text_physics <- data %>% filter(Category == "Physics") %>% select(Motivation)
text_chemistry <- data %>% filter(Category == "Chemistry") %>% select(Motivation)
text_medicine <- data %>% filter(Category == "Medicine") %>% select(Motivation)
text_literature <- data %>% filter(Category == "Literature") %>% select(Motivation)
text_economics <- data %>% filter(Category == "Economics") %>% select(Motivation) 

docs_peace <- Corpus(VectorSource(text_peace))
docs_physics <- Corpus(VectorSource(text_physics))
docs_chemistry <- Corpus(VectorSource(text_chemistry))
docs_medicine <- Corpus(VectorSource(text_medicine))
docs_literature <- Corpus(VectorSource(text_literature))
docs_economics <- Corpus(VectorSource(text_economics))

cleaning <- function(doc){
  doc <- doc %>%
    tm_map(removeNumbers) %>%
    tm_map(removePunctuation) %>%
    tm_map(stripWhitespace)
  doc <- tm_map(doc, content_transformer(tolower))
  doc <- tm_map(doc, removeWords, stopwords("english"))
}

docs_peace <- cleaning(docs_peace)
docs_physics <- cleaning(docs_physics)
docs_chemistry <- cleaning(docs_chemistry)
docs_medicine <- cleaning(docs_medicine)
docs_literature <- cleaning(docs_literature)
docs_economics <- cleaning(docs_economics)

word_cloud <- function(doc){
  dtm <- TermDocumentMatrix(doc) 
  matrix <- as.matrix(dtm) 
  words <- sort(rowSums(matrix),decreasing=TRUE) 
  df <- data.frame(word = names(words),freq=words)
}

df_peace <- word_cloud(docs_peace)
df_physics <- word_cloud(docs_physics)
df_chemistry <- word_cloud(docs_chemistry)
df_medicine <- word_cloud(docs_medicine)
df_literature <- word_cloud(docs_literature)
df_economics <-word_cloud(docs_economics)


#bigrams
bitoken <- function(doc){
  bigrams <- NGramTokenizer(doc, Weka_control(min = 2, max = 2))
  two_words <- data.frame(table(bigrams))
  two_words <- two_words %>% arrange(desc(Freq))
}

bigram_peace <- bitoken(docs_peace)
bigram_physics <- bitoken(docs_physics)
bigram_chemistry <- bitoken(docs_chemistry)
bigram_medicine <- bitoken(docs_medicine)
bigram_literature <- bitoken(docs_literature)
bigram_economics <- bitoken(docs_economics)
```


```{r wordclouds, echo=FALSE, warning = FALSE, message = FALSE, results=FALSE}
par(mfrow=c(2,3), mar=c(1,0.5,1,0.5))
wordcloud(words = df_chemistry$word, freq = df_chemistry$freq, min.freq = 1, max.words=15, random.order=FALSE, rot.per=0, colors=brewer.pal(7, "Oranges"), scale = c(2.2,0.25)) + title("Chemistry")

wordcloud(words = df_economics$word, freq = df_economics$freq, min.freq = 1, max.words=15, random.order=FALSE, rot.per=0, colors=brewer.pal(7, "Oranges"), scale = c(2.2,0.25)) + title("Economics")

wordcloud(words = df_literature$word, freq = df_literature$freq, min.freq = 1, max.words=15, random.order=FALSE, rot.per=0, colors=brewer.pal(7, "Oranges"), scale = c(2.2,0.25)) + title("Literature")

df_medicine <- df_medicine[-c(1,2),]
wordcloud(words = df_medicine$word, freq = df_medicine$freq, min.freq = 1, max.words=15, random.order=FALSE, rot.per=0, colors=brewer.pal(7, "Oranges"), scale = c(2.2,0.25)) + title("Medicine")

wordcloud(words = df_peace$word, freq = df_peace$freq, min.freq = 1, max.words=15, random.order=FALSE, rot.per=0, colors=brewer.pal(7, "Oranges"), scale = c(2.2,0.25)) + title("Peace")

df_physics <- df_physics[-c(1),]
wordcloud(words = df_physics$word, freq = df_physics$freq, min.freq = 1, max.words=15, random.order=FALSE, rot.per=0, colors=brewer.pal(7, "Oranges"), scale = c(2.2,0.25)) + title("Physics")
```


\newpage
And last but not least - most popular two-word combinations in the motivations (**bigrams**):

```{r bigram_clouds, echo=FALSE, warning = FALSE, message = FALSE, cache=FALSE, results=FALSE}
par(mfrow=c(2,3), mar=c(1,0.5,1,0.5))
wordcloud(bigram_chemistry$bigrams, bigram_chemistry$Freq, random.order = FALSE,
          scale = c(2,0.15), min.freq = 2, colors = brewer.pal(9, "Oranges"),
          max.words = 14, rot.per = 0) + title("Chemistry")
wordcloud(bigram_economics$bigrams, bigram_economics$Freq, random.order = FALSE,
          scale = c(2,0.15), min.freq = 2, colors = brewer.pal(9, "Oranges"),
          max.words = 9, rot.per = 0) + title("Economics")
wordcloud(bigram_literature$bigrams, bigram_literature$Freq, random.order = FALSE,
          scale = c(2,0.15), min.freq = 2, colors = brewer.pal(9, "Oranges"),
          max.words = 14, rot.per = 0) + title("Literature")
bigram_medicine <- bigram_medicine[-c(1),]
wordcloud(bigram_medicine$bigrams, bigram_medicine$Freq, random.order = FALSE,
          scale = c(2,0.15), min.freq = 2, colors = brewer.pal(9, "Oranges"),
          max.words = 14, rot.per = 0) + title("Medicine")
wordcloud(bigram_peace$bigrams, bigram_peace$Freq, random.order = FALSE,
          scale = c(2,0.15), min.freq = 2, colors = brewer.pal(9, "Oranges"),
          max.words = 19, rot.per = 0) + title("Peace")
wordcloud(bigram_physics$bigrams, bigram_physics$Freq, random.order = FALSE,
          scale = c(2,0.15), min.freq = 2, colors = brewer.pal(9, "Oranges"),
          max.words = 13, rot.per = 0) + title("Physics")

```

